---
title: "RSVI"
author: "Paula and Beni"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
# output:
#   pdf_document:
#     toc: true
#     toc_depth: 2
header-includes:
   - \usepackage{amsmath}
# bibliography: bibliography.bib
---

```{r}
source("MOD09_MODOC_filter.R")
source("remove_outliers.R")
source("gather_data.R")
source("align_events.R")
source("rsvi_sites.R")
source("add_scaled_rsvi.R")
source("add_normalised_rsvi.R")
source("get_consecutive.R")

library(dplyr)
library(lubridate)
library(readr)
library(ggplot2)
library(caret)
library(randomForest)
```

## Gather data: site-specific CSV files downloaded by Adria
- Function "MOD09_MODOC_filter" combines MOD09GA and MODOCGA products for all sites (one CSV for each FLUXNET site) into one. The output is a csv file o it is in "MOD09GA_MODOCGA_filter_indices.Rdata" file (for more information see README - "MODIS Data information")
```{r}
# path <- "C:/Users/Paula/Desktop/Pau/Ecologia terrestre/rsvi/data/FLUXNET_MODOCGA_MOD09GA1km_2000_2018/"
# ddf <- MOD09_MODOC_filter(path_files=path, QC500_filter="no")
# ddf <- gather_data(ddf, add_scaled = FALSE, file="df") %>% ungroup()
```

## Get data

Load all RSVI data from .Rdata file. Preprocessed by Paula.
```{r}
## change path to file by hand here
path <-"C:/Users/Paula/Desktop/Pau/Ecologia terrestre/rsvi/data/"
# ddf <- gather_data("/alphadata01/bstocker/data/modis_MOD09GA1km_fluxnet_cutouts/MOD09GA_MODOCGA_filter_indices.RData")
ddf <- gather_data("C:/Users/Paula/Desktop/Pau/Ecologia terrestre/rsvi/data/MOD09GA_MODOCGA_filter_indices.Rdata", add_scaled = FALSE) %>%
  ungroup()
```

## Site selection

Subset homogenous sites. Selection of sites is based on whether sites could be allocated to clusters in Stocker et al. (2018) and based on the selection by Manuela Balzarolo (see `site_selection_rsvi.Rmd`).
```{r}
df_homo <- read_csv("./data/sites2.csv")
ddf <- ddf %>% filter( site %in% df_homo$sitename )
df_homo$sitename
```
## Scaling

Scaling is done with respect to the full time series of the RSVIs, not just the subset of data points just before and during drought events. Two methods are implemented:

- `"range"`: scales by range to within 0 and 1, where the range is from all values from all sites and dates.
- `"range_bysite"`: scales by range to within 0 and 1 by site, where the range is from values for each site separately.
```{r}
dovars <- c("cci", "evi", "ndvi", "NIRv", "pri")
ddf <- ddf %>%
  dplyr::select(site, date, one_of(dovars)) %>%
  add_scaled_rsvi(dovars, method="range_bysite") 
```
## Complement data

Add fLUE data.
```{r}
## Get fLUE Stocker et al., 2018 publicly available data here: https://zenodo.org/record/1158524#.W_bNMZNKjOQ
ddf <- read_csv("data/flue_stocker18nphyt.csv") %>% #/alphadata01/bstocker/data/flue/ (Benjamin)
  select(site, date, flue, is_flue_drought) %>%
  right_join(ddf, by=c("site", "date"))
# save(ddf, file = "./data/ddf_v4.Rdata")
```

## Align by drought event
```{r}
## Get fLUE Stocker et al., 2018 publicly available data here: https://zenodo.org/record/1158524#.W_bNMZNKjOQ
df_flue <- readr::read_csv( "data/flue_stocker18nphyt.csv" ) %>%
  dplyr::select(-year, -doy, -cluster) %>%
  dplyr::rename( isevent = is_flue_drought )

# ONLY 5 classes:
subveg <- c("GRA","SAV","DBF","EBF","ENF")

# XXX I've changed align_events because flue data was already on ddf
ddf1 <- ddf %>% dplyr::rename( isevent = is_flue_drought )

## Rearrange data
out_align <- align_events(
  ddf1,
  select(df_flue, site, date, isevent),
  dovars,
  leng_threshold=10, 
  before=20, after=80, nbins=10
  )

## Plots
# ##  Raw data, aligned by drought events
# out_align$df_dday %>% #filter(site == sitename) %>%
#   ggplot(aes(x=dday, y=ndvi)) +
#   geom_line(aes(group=inst)) +
#   theme_bw() +
#   facet_wrap(~site, scales = "free_y") + ggtitle("RSVI")
# 
# ##  dsRSVI data, aligned by drought events
# out_align$df_dday %>% #filter(site == sitename) %>%
#   ggplot(aes(x=flue, y=ndvi)) +
#   geom_point(aes(group=inst)) +
#   theme_bw() +
#   facet_wrap(~site, scales = "free_y") + ggtitle("sdRSVI")

```
Not clear to me why the curve is not centered around 1 for dday between -10 and 0 (zero-bin). Division by median of value in zero-bin is done in `align_events()`.

## Plots aligned by site

Data is aggregated across multiple drought events (column `inst`).
```{r}
median <- out_align$df_dday_agg_inst %>%
  select(site, dday, ends_with("median")) %>%
  tidyr::gather(rsvi, median, ends_with("median")) %>%
  mutate(rsvi=stringr::str_replace(rsvi, "_median", "") )
q33 <- out_align$df_dday_agg_inst %>%
  select(site, dday, ends_with("q33")) %>%
  tidyr::gather(rsvi, q33, ends_with("q33")) %>%
  mutate(rsvi=stringr::str_replace(rsvi, "_q33", "") )
q66 <- out_align$df_dday_agg_inst %>%
  select(site, dday, ends_with("q66")) %>%
  tidyr::gather(rsvi, q66, ends_with("q66")) %>%
  mutate(rsvi=stringr::str_replace(rsvi, "_q66", "") )
df_dday_agg_inst <- median %>%
  left_join(q33, by=c("site","dday", "rsvi")) %>%
  left_join(q66, by=c("site","dday", "rsvi"))

## Example for one site
name_site <- "AU-DaP"

df_dday_agg_inst %>%
  filter(site==name_site) %>%
  filter(rsvi %in% c("flue","sndvi", "sevi", "scci", "spri", "sNIRv")) %>%
  ggplot(aes(x=dday, y=median)) +
  geom_line() + theme_classic() +
  labs(x="Day after drought onset", y="Unitless") + ggtitle(name_site) +
  geom_ribbon(aes(ymin=q33, ymax=q66), alpha=0.3) +
  facet_wrap( ~ rsvi)
```


## Plot aligned and aggregated sites

Absolute values, aggregated across sites and events
```{r}
median <- out_align$df_dday_agg_inst_site %>%
  select(dday, ends_with("median")) %>%
  tidyr::gather(rsvi, median, ends_with("median")) %>%
  mutate(rsvi=stringr::str_replace(rsvi, "_median", "") )
q33 <- out_align$df_dday_agg_inst_site %>%
  select(dday, ends_with("q33")) %>%
  tidyr::gather(rsvi, q33, ends_with("q33")) %>%
  mutate(rsvi=stringr::str_replace(rsvi, "_q33", "") )
q66 <- out_align$df_dday_agg_inst_site %>%
  select(dday, ends_with("q66")) %>%
  tidyr::gather(rsvi, q66, ends_with("q66")) %>%
  mutate(rsvi=stringr::str_replace(rsvi, "_q66", "") )
df_dday_agg_inst_site <- median %>%
  left_join(q33, by=c("dday", "rsvi")) %>%
  left_join(q66, by=c("dday", "rsvi"))

df_dday_agg_inst_site %>%
     filter(rsvi %in% c("flue")) %>% # "flue",
     mutate(rsvi=factor(rsvi,levels=c("flue"))) %>% #"flue"
     ggplot(aes(x=dday, y=median)) +
     geom_hline(yintercept=1,col="gray") +
     theme_classic() +
     annotate("rect", xmin = 0, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = .25)  +
     # annotate("rect", xmin = 20, xmax = 40, ymin = -Inf, ymax = Inf, alpha = .25)  +
   # annotate("rect", xmin = 40, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = .10)  +
     geom_line(aes(color=rsvi)) +
     labs(x="Day after drought onset", y="Unitless") +
     geom_ribbon(aes(ymin=q33, ymax=q66, fill=rsvi), alpha=0.3) +
     scale_color_brewer(palette="Dark2") +
     scale_fill_brewer(palette="Dark2") +
     scale_y_continuous(breaks = c(0,0.5,1)) +
     scale_x_continuous(limits = c(-10,75)) +
     theme_classic() +
     theme(axis.text=element_text(size=12, color="black"),
           axis.title=element_text(size=14),
           panel.border = element_rect(colour = "black", fill=NA),
           legend.position="none") 
```

## Plot RSVI - fLUE
```{r}
# RSVI
df_dday_agg_inst_site %>%
  filter(rsvi %in% c("flue","ndvi", "evi", "cci", "pri", "NIRv")) %>%
      mutate(rsvi=factor(rsvi,levels=c("flue","ndvi", "evi", "cci", "pri", "NIRv")))  %>%
  ggplot(aes(x=dday, y=median)) +
  theme_classic() +
  geom_line(aes(color=rsvi)) +
  labs(x="Day after drought onset", y="Unitless") +
  geom_ribbon(aes(ymin=q33, ymax=q66, fill=rsvi), alpha=0.3) +
  scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Dark2") +
  facet_wrap(~rsvi, scales = "free_y")

# scaled RSVI
df_dday_agg_inst_site %>%
  filter(rsvi %in% c("flue","sndvi", "sevi", "scci", "spri", "sNIRv")) %>%
    mutate(rsvi=factor(rsvi,levels=c("flue","sndvi", "sevi", "scci", "spri", "sNIRv"))) %>%
  ggplot(aes(x=dday, y=median)) +
  geom_line(aes(color=rsvi)) +
  theme_classic() +
  labs(x="Day after drought onset", y="Unitless") +
  geom_ribbon(aes(ymin=q33, ymax=q66, fill=rsvi), alpha=0.3) +
  scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Dark2") +
  facet_wrap(~rsvi, scales = "free_y")

# Scaled and normalized RSVI
dose.labs <- c("flue" = "fLUE",
               "dsndvi" = "dsNDVI",
               "dsevi" = "dsEVI",
               "dscci" = "dsCCI",
               "dspri" = "dsPRI",
               "dsNIRv" = "dsNIRv")
df_dday_agg_inst_site %>%
  filter(rsvi %in% c("flue","dsndvi", "dsevi", "dscci", "dspri", "dsNIRv")) %>% # "flue",
      mutate(rsvi=factor(rsvi,levels=c("flue","dsndvi", "dsevi","dscci", "dspri", "dsNIRv"))) %>% #"flue"
  ggplot(aes(x=dday, y=median)) +
  geom_hline(yintercept=1,col="gray") +
  theme_classic() +
  annotate("rect", xmin = 0, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = .25)  +
  # annotate("rect", xmin = 20, xmax = 40, ymin = -Inf, ymax = Inf, alpha = .25)  +
  # annotate("rect", xmin = 40, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = .10)  +
  geom_line(aes(color=rsvi)) +
  labs(x="Day after drought onset", y="Unitless") +
  geom_ribbon(aes(ymin=q33, ymax=q66, fill=rsvi), alpha=0.3) +
  scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Dark2") +
  scale_y_continuous(breaks = c(0.5,1,1.5)) +
  scale_x_continuous(limits = c(-10,75)) +
  facet_wrap(~rsvi, labeller = as_labeller(dose.labs))  + theme_classic() +
    theme(axis.text=element_text(size=12, color="black"),
        axis.title=element_text(size=14),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none") 

```

## Plot by vegetation type
- Add vegetation type and meteorological variables to data and do evaluations with data aggregated by vegetation type - the way you've done it before.
```{r}
## Vegetation type - add info
load(paste(path,"metainfo_sites_fluxnet2015.Rdata",sep=""))
metainfo_sites_fluxnet2015 <- as_tibble(metainfo_sites_fluxnet2015)

## Complement the data with meteorological variables, measured at the FLUXNET sites.
load("data/obs_eval_NT.Rdata") # adjust path /Users/benjaminstocker/eval_pmodel/

# set of RSVI:
vars <- c("flue","dsndvi", "dsevi", "dscci", "dspri", "dsNIRv")
vars_names <- c("flue","dsNDVI", "dsEVI", "dsCCI", "dsPRI", "dsNIRv")

df_dday_agg_inst_veg <- merge(df_dday_agg_inst, metainfo_sites_fluxnet2015[,c(1,5)], by.x="site", by.y="mysitename")

## Join SAV + WSA
df_dday_agg_inst_veg$classid[df_dday_agg_inst_veg$classid == "WSA"] <- "SAV"

nclass <- unique(df_dday_agg_inst_veg$classid)

# Median by classid (nomalized on 1)
dose.labs <- vars_names
names(dose.labs) <- vars

df_dday_agg_inst_veg %>%  group_by( dday, classid, rsvi ) %>%
  summarise_at( vars(one_of("median","q33","q66")), funs(median( ., na.rm=TRUE))) %>%
  filter( !is.na( dday ) ) %>% filter(classid %in% c("ENF","SAV","GRA","EBF", "DBF")) %>% #,"MF","CRO"
  filter(rsvi %in% vars)  %>% 
      mutate(rsvi=factor(rsvi,levels=vars)) %>%
  ggplot(aes(x=dday, y=median, group=classid)) + # If we want the different sites: ,group=site
  geom_vline(xintercept=0,col="gray") + geom_hline(yintercept=1,col="gray") +
  geom_line(aes(color=rsvi)) + geom_ribbon(aes(ymin=q33, ymax=q66, fill=rsvi), alpha=0.35) +
  # xlim(-10, 40) +
  theme_classic() +
  scale_x_continuous(limits=c(-10,75)) +
  scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Dark2") +
  theme(axis.text=element_text(size=12, color="black"),
        axis.title=element_text(size=14),
        panel.border = element_rect(colour = "black", fill=NA),
        strip.text.x = element_text(size = 12),
        strip.text.y = element_text(size = 12),
        legend.position = "none", legend.title = element_blank()) +
    annotate("rect", xmin = 0, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = .15) +
  facet_grid(rsvi~classid, labeller = labeller(rsvi = dose.labs)) + #,  scales = "free_y" /
  labs(x="Day after drought onset", y="Unitless")


```
## Plot Forest vs Non-Forest
- Add vegetation type and meteorological variables to data and do evaluations with data aggregated by vegetation type - the way you've done it before.
```{r}
## BIOMES
forest <- c("DBF","EBF","ENF")
nonforest <- c("SAV","WSA","GRA")

df_dday_agg_inst_veg$biome[df_dday_agg_inst_veg$classid %in% forest] <- "Forest"
df_dday_agg_inst_veg$biome[df_dday_agg_inst_veg$classid %in% nonforest] <- "Non-Forest"

nbiomes <- unique(df_dday_agg_inst_veg$biome)

# # Median by classid (nomalized on 1)
# dose.labs <- vars_names
# names(dose.labs) <- vars

df_dday_agg_inst_veg %>%  group_by( dday, biome, rsvi ) %>%
  filter(!is.na(biome)) %>%
  summarise_at( vars(one_of("median","q33","q66")), funs(median( ., na.rm=TRUE))) %>%
  filter( !is.na( dday ) )%>% 
  filter(rsvi %in% vars)  %>% 
      mutate(rsvi=factor(rsvi,levels=vars)) %>%
  ggplot(aes(x=dday, y=median, group=rsvi)) +
  geom_vline(xintercept=0,col="gray") + geom_hline(yintercept=1,col="gray") +
  geom_line(aes(color=rsvi)) + #geom_ribbon(aes(ymin=q33, ymax=q66, fill=rsvi), alpha=0.35) +
  geom_smooth(aes(color=rsvi)) +
  theme_classic() +
  scale_x_continuous(limits=c(-5,50)) +
  scale_color_brewer(palette="Dark2") +
  scale_fill_brewer(palette="Dark2") +
  theme(axis.text=element_text(size=12, color="black"),
        axis.title=element_text(size=14),
        panel.border = element_rect(colour = "black", fill=NA)
        # strip.text.x = element_text(size = 12),
        # strip.text.y = element_text(size = 12),
        # legend.position = "none", legend.title = element_blank()
        ) +
    annotate("rect", xmin = 0, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = .15) +
  facet_grid(~biome) + #,  scales = "free_y" /
  labs(x="Day after drought onset", y="Unitless")


```


## Plot time series with all predictors
- Complement data with meteorological variables, measured at the FLUXNET sites
```{r}
sitios <- ddf$site %>% unique()

# pdf(paste("Times_series.pdf",sep=""),width=10.84,height=5.30)
for(i in 1:length(sitios)){
# i <- 11 # Nice Time series
sitename <- sitios[i]
ddfsite <- ddf %>% filter(site == sitename) %>%
left_join(rename(obs_eval_NT$ddf, site=sitename), by=c("site", "date")) %>%
    mutate (PPFD = ppfd_fluxnet2015 * fapar) 

# class <- unique(ddfsite$classid)


ts <- ddfsite %>% 
  tidyr::gather(variables, value, c(flue, ndvi, evi, cci, pri, NIRv)) %>% # ,temp,PPFD
  filter(site==sitename) %>% 
  mutate(variables=factor(variables,levels=c("flue","ndvi", "evi", "cci", "pri", "NIRv"))) %>% #,"temp","PPFD"
  filter(!is.na(variables))

# New facet label names for dose variable
dose.labs <- c("flue" = "fLUE",
               "ndvi" = "NDVI",
               "evi" = "EVI",
               "cci" = "CCI",
               "pri" = "PRI",
               "NIRv" = "NIRv"
               # "temp" = "Temp",
               # "PPFD" = "APAR"
               )

flue_droughts <-  get_consecutive(ddfsite$is_flue_drought) 
if (nrow(flue_droughts)>0) {
flue_droughts$date_start <- ddfsite$date[flue_droughts$idx_start]
flue_droughts <- flue_droughts %>%  mutate(date_end = date_start + len) 

# Zoom where flue data is available
# flue_dates <- ts %>% filter(variables=="flue") %>% select(date) %>% unlist()
# flue_dates <- c(flue_dates[1],flue_dates[length(flue_dates)])

print(ggplot(ts, aes(x=date, y=value)) +
    facet_grid(rows=vars(variables), scales = "free_y", labeller = as_labeller(dose.labs)) +
    geom_rect(
    data = flue_droughts, 
    aes(x = NULL,y = NULL, xmin=date_start, xmax=date_end, ymin=-Inf, ymax=Inf),
    fill=("gray"), alpha=0.7, #rgb(0,0,0,0.3) #"#e8c745"
    color=NA) +
    geom_line() + 
    theme_classic() + 
    ggtitle(paste(sitename,class,sep="  ")) + #-
  scale_x_date(limits = as.Date(c('2000-01-01','2015-01-01'))) + labs(x="Date"))
}else{
 print(ggplot(ts, aes(x=date, y=value)) +
    facet_grid(rows=vars(variables), scales = "free_y", labeller = as_labeller(dose.labs))  +
    geom_line() + 
    theme_classic() + 
    ggtitle(sitename)  +
  scale_x_date(limits = as.Date(c('2000-01-01','2015-01-01'))) + labs(x="Date"))
}

}
# dev.off()
```
## Join SAV + WSA
- Complement the data with vegetation class
```{r}
# vegetation
metainfo_sites_fluxnet2015 <- metainfo_sites_fluxnet2015 %>% rename(site=mysitename)

ddf <- ddf %>% 
  inner_join(metainfo_sites_fluxnet2015[,c(1,5)], by="site") 

## Join SAV + WSA 
ddf$classid[ddf$classid == "WSA"] <- "SAV"
```
## Drought vs No-Drought days
- According to this evaluation, CCI and PRI vary very little during drought conditions but are clearly correlated with other RSVIs. Is this correlation affected whether data is in a drought or not? Below a quick look at how EVI and PRI are correlated and how this relationship is affected by the factor `is_flue_drought`. There might be some information here...
```{r}
day <- c("TRUE" = "Drought",
         "FALSE" = "No-Drought")

ddf %>% 
  filter(!is.na(is_flue_drought)) %>% 
  ggplot(aes(x=evi, y=NIRv, color=is_flue_drought)) +
  scale_colour_discrete(name  = NULL) +
  theme_classic() + 
    theme(axis.text=element_text(size=12, color="black"),
        axis.title=element_text(size=14),
        legend.text = element_text(size = 12),
        panel.border = element_rect(colour = "black", fill=NA)) +
  guides(colour = guide_legend(override.aes = list(size=3))) +
  # facet_grid(classid~is_flue_drought, labeller = labeller(is_flue_drought = as_labeller(day))) +
  # facet_wrap(~classid) +
  labs(x="NDVI", y="NIRv") +
  # geom_point(alpha=0.2, shape=20) + scale_color_grey()
  geom_point(alpha=0.2, shape=20) + scale_color_brewer(palette="Set1",direction = -1,
                                                       name = NULL, labels = c("Non-drought","Drought"))

####
    data <- ddf %>%
      filter(!is.na(is_flue_drought)) 
    
# Index vs Index
lm_eqn = function(df){
    m = lm(pri ~ evi, df);
    eq <- substitute( 
      # italic(y) == a + b %.% italic(x)*","~~italic(R)^2~"="~2*","~~italic(p)~"="~pv,
      italic(R)^2~"="~r2*","~~italic(p)~"="~pv,
                     list(a = format(coef(m)[1], digits = 2), 
                          b = format(coef(m)[2], digits = 2), 
                          r2 = format(summary(m)$r.squared, digits = 2),
                          pv = format(summary(m)$coefficients[8], digits=2)))
    
    as.character(as.expression(eq));                 
  }

    library(plyr) 
    eq <- ddply(data,.(is_flue_drought),lm_eqn) # por clasificación
    eqtotal <- ddply(data,.(),lm_eqn) # correlación general

  ggplot(data, aes(x=evi, y=pri, group=is_flue_drought, color=is_flue_drought)) +
  geom_point(alpha=0.5, shape=20) + 
  # scale_color_brewer(palette="Set1",direction = -1,name = NULL, labels = c("Non-drought","Drought")) +
  # scale_colour_manual(values=cbp1) + 
  scale_color_grey(start = 0.8, end = 0.2, labels = c("Non-drought","Drought")) +
  geom_smooth(aes(linetype=is_flue_drought), color="black", 
              method = "lm", se=FALSE, formula = y ~ x) + 
  theme_classic() + 
  geom_text(data=eq[2,],aes(x = 0.25, y = 0.05,label=V1), # VERDADERO
            cex=5, parse = TRUE, inherit.aes=FALSE) +
  geom_text(data=eq[1,],aes(x = 0.8, y = 0.05,label=V1), # FALSO
            cex=5, parse = TRUE, inherit.aes=FALSE) +
  theme(axis.text=element_text(size=12, color="black"),
        axis.title=element_text(size=14),
        legend.text = element_text(size = 12),
        panel.border = element_rect(colour = "black", fill=NA)) +
  guides(colour = guide_legend(override.aes = list(size=3))) +
  labs(x="NDVI", y="PRI") #+ 
  # scale_y_continuous(limits = c(-1, 1)) + 
  # scale_x_continuous(limits = c(-1, 1))

```

## Time series decouple
```{r}
# Add normalised RSVIs
sdovars <- paste0("s", dovars)
ddf <- ddf %>% add_normalised_rsvi(sdovars, out_align$norm) 

# Site:
egSite <- "AU-DaP"# "FR-LBr" #"IT-Ro1"#

# Indices
egSite_data <- ddf %>% filter(site == egSite) %>%
  filter(!is.na(dsndvi)) %>% filter(!is.na(dsNIRv))

# Running windows for every date
library(stats)
rwndvi <- runmed(egSite_data$dsndvi,k=3)
rwcci <- runmed(egSite_data$dsNIRv,k=3)

# Drought
df_dday <- out_align$df_dday
time_d <- df_dday[which(df_dday$dday==0 & df_dday$site==egSite),2]

# Plots
plot(egSite_data$date,as.vector(rwndvi),type="l",
     xlab="Date", ylab="Normalised NDVI (CCI)", 
     # ylim=c(),
     lwd = 1)
lines(egSite_data$date,rwcci,col=2, lwd = 1)
abline(v = unlist(time_d), col="gray80")

```

## DROUGHT PREDICTION
```{r}
require( randomForest )
require( caret )
require( tidyverse )

# load data and RF function
load("./data/ddf_v4.Rdata")
load("./data/metainfo_Tier1_sites_kgclimate_fluxnet2015.Rdata")
load("./data/obs_eval_NT.Rdata") #

source("analyse_modobs2.R")
source("wrap_ml.R")

# complement info using the meta info of FLUXNET sites provided through rsofun
ddf <- ddf %>% 
  left_join(metainfo_Tier1_sites_kgclimate_fluxnet2015 %>% select(site=sitename, classid), by = "site")

dovars <- c("cci","evi","ndvi","NIRv","pri") 

# Prepare data set
ddf_rf <- ddf %>% 
  left_join(rename(obs_eval_NT$ddf, site=sitename), by=c("site", "date")) %>%
  mutate (APAR = ppfd_fluxnet2015 * fapar) %>%  
  filter(!is.na(flue)) %>%
  select(site, is_flue_drought, flue, dovars, APAR, temp, classid) %>% 
  mutate(classid=factor(classid), is_flue_drought = factor(is_flue_drought))  %>% 
  drop_na()

# Class id: ONLY 5 classes
ddf_rf$classid[ddf_rf$classid=="WSA"] <- "SAV"
cv <- c("ENF","DBF","GRA","EBF","SAV")

ddf_sub <- ddf_rf %>% 
  filter(classid %in% cv) %>% droplevels()

sites <- ddf_sub$site %>% unique() 

## Predictors combinations
complete <- c("ndvi",    "evi",     "cci",     "pri",     "NIRv",    "APAR", "temp", "classid")
rsvi <- c("ndvi",    "evi",     "cci",     "pri",     "NIRv")
model3 <- c("ndvi",  "cci",  "temp", "classid")
model4 <- c("ndvi", "cci", "temp", "APAR")
model10 <- c("NIRv", "cci", "pri", "ndvi", "temp", "classid")
model11 <- c("NIRv", "pri", "temp", "classid")
estructura <- c("ndvi",    "evi",  "temp", "classid")
actividad <- c("pri",    "cci",  "temp", "classid")
model14 <- c("pri",    "NIRv",  "APAR", "classid")

# Each RSVI alone
ndvi <- c("ndvi")
evi <- c("evi")
cci <- c( "cci")
pri <- c("pri")
NIRv <- c("NIRv")

predictores <-list(complete, rsvi, model3, model4, ndvi, evi, cci, pri, NIRv, 
                   model10, model11, 
                   estructura, actividad, model14)


```

## Recursive feature elimination
```{r}
## See https://topepo.github.io/caret/recursive-feature-elimination.html
## Look at how model performance changes for different sets of predictors.

# Define folds and target
nam_group = "site"
nam_target = "is_flue_drought"

subsets <- complete %>% length() %>% seq() %>% rev()
# sites <- unique(df[[ "site" ]]) # 'nam_group' is site in this case (i.e. split the data by sparing data from one site for testing)
group_folds <- vector(mode = "list", length = length(sites))

for (i in seq_along(sites)) group_folds[[i]] <- which(ddf_sub[[nam_group]] != sites[i])
names(group_folds) <- paste0("Subject", sites)

# proProces for Quantitative analysis
if(nam_group("flue")){
normalization <- preProcess(ddf_sub, c("center", "scale"))
ds <- predict(normalization, ddf_sub)
ds <- as.data.frame(ds)
}else{ds <- ddf_sub}

ctrl <- rfeControl(functions = lrFuncs, # lrFuncs para is_flue_drought
                   method = "LGOCV",
                   index = group_folds,
                   repeats = 5,
                   verbose = FALSE
                   # rerank = TRUE
)

forml  <- as.formula(  paste( nam_target, "~", paste( complete, collapse=" + " ) ) )

set.seed(10)
lmProfile <- caret::rfe( forml,
                         df,
                         method="nnet",
                         sizes = c(1:12),
                         rfeControl = ctrl
)

lmProfile$fit
lmProfile$optVariables
head(lmProfile$variables)
predictors(lmProfile)
# head(lmProfile$resample)
trellis.par.set(caretTheme())
plot(lmProfile, type = c("g", "o"))
lmProfile$metric

```

## CLASSIFICATION
```{r}

for(i in  lenght(predictores)){ 
rf_lgocv <- wrap_ml( df = ddf_sub, 
                                nam_target = "is_flue_drought", 
                                nam_group = "site",
                                method =  "nnet",
                                train_method = "LGOCV",
                                predictors = predictores[[i]],  
                                tune = TRUE,
                                inner = TRUE,
                                classification = TRUE
)
# save(rf_lgocv , file = paste("./data/NN_isFlue_mod",i,".Rdata",sep=""))
print(rf_lgocv$rf$results) # Promising: has accuracy of 0.81. 
}

print(paste("Accuracy of main model:", rf_lgocv$rf$results$Accuracy))
print(paste("Mean accuracy across leave-site-out models:", purrr::map_dbl(rf_lgocv$list_rf, "myresults") %>% mean()))

## Test: How is accuracy calculated?
get_modobs <- function(df){
  tibble(mod = as.vector(df$pred), obs = df$obs)
}
list_modobs_listmodels <- purrr::map(rf_lgocv$list_rf, ~get_modobs(.))

calc_performance <- function(df){
  df_sum <- df %>% 
    dplyr::mutate(good = obs==mod) %>% 
    dplyr::summarise(good = sum(good))
  df_sum$good / nrow(df)
}
acc_test <- purrr::map_dbl(list_modobs_listmodels, ~calc_performance(.)) %>% mean()  
# that's the same as given above as 'Mean accuracy across leave-site-out models'
print(paste("Re-calculated mean accuracy across leave-site-out models:", acc_test))

## Construct confusion matrix
cm_simple <- list_modobs_listmodels %>% bind_rows() %>% table()
df_modobs_listmodels <- list_modobs_listmodels %>% bind_rows()
cm <- confusionMatrix( data = as.factor(df_modobs_listmodels$mod), 
                       reference = as.factor(df_modobs_listmodels$obs), positive="TRUE")

source('ConfusionMatrix.R')
draw_confusion_matrix(cm)

## Show results for each site (prediction trained at all other sites)
vec_acc <- purrr::map_dbl(rf_lgocv$list_rf, "myresults")
df_acc <- tibble(site = sites, accuracy = vec_acc )
print("Accuracy for each site (prediction trained at all other sites):")
print(df_acc)

## Get variable importance (see https://topepo.github.io/caret/variable-importance.html)
var_imp <- varImp(rf_lgocv$rf)
list_var_imp <- purrr::map(rf_lgocv$list_rf, ~varImp(.))
plot(var_imp)

## Alternative: GARSON FOR NN
# library(NeuralNetTools)
# garson(rf_lgocv$rf$finalModel)
```

## Time series mod-obs 
```{r}
siteobj <-  "AU-DaP" # "IT-Ro1"
s <- list_modobs_listmodels[[siteobj]]
#Algunos sitios no coincide el número de observaciones, rastrear fecha para graficar
# p <- rf_lgocv$list_rf$`FR-Pue`$pred
# s <- ddf %>% 
#   left_join(rename(obs_eval_NT$ddf, site=sitename), by=c("site", "date")) %>%
#   filter(!is.na(flue)) %>%
#   filter(site == siteobj) %>%
#   select(date, is_flue_drought) %>% 
#   rename(obs = is_flue_drought)  %>% 
#   drop_na()
s$obs <- as.character(s$obs)

time_series <- ddf %>% filter(site==siteobj) %>% filter(!is.na(flue)) %>% drop_na() %>%
  select(date, flue) %>% cbind(s) %>% # left_join(s, by="date")
  gather(key=variable, drought, -date, -flue) 
# time_series$variable <- as.factor(time_series$variable)
# time_series$drought <- factor(time_series$drought, 
#                               levels=c("TRUE", "FALSE"), labels=c("Drought", "No-Drought"))

time_series$variable[time_series$variable=="mod"] <- 1
time_series$variable[time_series$variable=="obs"] <- 2
time_series$drought[time_series$drought=="TRUE"] <- 0
time_series$drought[time_series$drought=="FALSE"] <- 1
time_series$variable <- as.factor(time_series$variable)
time_series$drought <- as.numeric(time_series$drought)

# Bien clasificados:
ts <- ddf %>% filter(site==siteobj) %>% filter(!is.na(flue)) %>% drop_na() %>%
  select(date, flue) %>% cbind(s)  # left_join(s, by="date")
bienclas <- ts[which(ts$mod==ts$obs),]
bienclas$mod <- "mod"
colnames(bienclas) <- c("date","flue","variable", "drought" )

bienclas$variable[bienclas$variable=="mod"] <- 1
bienclas$drought[bienclas$drought=="TRUE"] <- 0
bienclas$drought[bienclas$drought=="FALSE"] <- 1
bienclas$variable <- as.factor(bienclas$variable)
bienclas$drought <- as.numeric(bienclas$drought)

# PLOT
linecolors <- c("#8c8c8c","#000000")
fillcolors <- c("#8c8c8c","#000000")

ggplot(data=time_series, aes(x=date, y=drought, colour = variable, fill = variable)) +
  # geom_point(shape = 21, alpha = 0.5, size = 2.5) +
  scale_color_manual(values=linecolors, name = "Classification", labels = c("Mod", "Obs")) +
  scale_fill_manual(values=fillcolors, name = "Classification", labels = c("Mod", "Obs")) +
  geom_line(data=time_series, aes(x=date, y=flue), color="black") + 
  geom_point(data=bienclas, aes(x=date,y=drought), color="red", size = 2.5) +
  scale_y_continuous(NULL, 
                     sec.axis = sec_axis(~., name = "fLUE"),
                     breaks=c(0,1), labels = c("Drought","No-Drought")) +
  xlab("Date") +
  theme_classic() +
  theme(axis.text=element_text(size=12, color="black"),
  axis.title=element_text(size=14),
  panel.border = element_rect(colour = "black", fill=NA)) 

cm <- confusionMatrix( data = as.factor(ts$mod), 
                       reference = as.factor(ts$obs), positive="TRUE")
```

## Inside vegetation class
```{r}
for(v in 1:length(cv)){
  ddf_veg <- ddf_sub %>% filter(classid == veg[v])
  
  # for(i in 1:3){ # lenght(predictores)
    rf_lgocv <- wrap_ml( df = ddf_veg, 
                         nam_target = "flue", #"is_flue_drought", 
                         nam_group = "site",
                         method = "nnet",
                         train_method = "LGOCV",
                         predictors = predictores[[1]],  # use double square bracket here to access element of list
                         tune = TRUE,
                         inner = TRUE,
                         classification = FALSE
    )
    # save(rf_lgocv , file = paste("./data/NN_InsideVeg_isFlue_mod",i,".Rdata",sep=""))
    print(v)
    print(varImp(rf_lgocv$rf))
    print(rf_lgocv$rf$results) 
  # }
}

```

## DROUGHT MAGNITUDE
```{r}
for(i in 1:length(predictores)){ # lenght(predictores)
rf_lgocv_flue <- wrap_ml( df = ddf_sub, 
                          method = "nnet",
                          nam_target = "flue", 
                          nam_group = "site",
                          train_method = "LGOCV",
                          predictors = predictores[[i]],  # use double square bracket here to access element of list
                          tune = FALSE, #TRUE,
                          inner = TRUE,
                          classification = FALSE
)
print(paste("Results of main model:"))
print(rf_lgocv_flue$rf$results)   # RMSE 0.1765139   R2 0.3186167
print(i)
# save(rf_lgocv_flue , file = paste("./data/NN_Flue_mod",i,".Rdata",sep=""))
}

## B: Mod vs obs for leave-group-out models, evaluated at left-out site data
## Note: it's necessary to set 'inner' = TRUE in the wrap_ml() call to get all this data
## ==> Note: much worse performance than suggested above. 
## Important: The performance of the pooled model (shown here) is not the same as the 
## mean across individual models from left-out sites.
get_modobs <- function(df){
  tibble(mod = as.vector(df$pred), obs = df$obs)
}
list_modobs_listmodels <- purrr::map(rf_lgocv_flue$list_rf, ~get_modobs(.))
out_modobs <- list_modobs_listmodels %>%
  bind_rows %>% 
  analyse_modobs2(mod = "mod", obs = "obs")
out_modobs$gg

# This gives almost the same results as the summary of the main model 
results_by_listmodels <- purrr::map(list_modobs_listmodels, ~analyse_modobs2(.)) %>% 
  purrr::map_dfr(., "results") %>% 
  dplyr::summarise_all(.funs = mean)

# Alternative
results_by_listmodels <- purrr::map(list_modobs_listmodels, ~analyse_modobs2(.)) %>% 
  purrr::map_dfr(., "df_metrics") %>% data.frame() %>% filter(.metric == "rsq") %>%
  select( .estimate ) %>% filter(!is.na(.estimate)) %>%
  dplyr::summarise_all(.funs = mean)

print(results_by_listmodels)
print(rf_lgocv_flue$rf$results)

# Rsq for each site
results_by_site <- purrr::map(list_modobs_listmodels, ~analyse_modobs2(.)) %>% 
  purrr::map_dfr(., "df_metrics") %>% data.frame() %>% filter(.metric == "rsq") %>%
  select( .estimate )

###### Density  ########
library(viridis)
theme_set(theme_bw(base_size = 16))
get_density <- function(x, y, ...) {
  dens <- MASS::kde2d(x, y, ...)
  ix <- findInterval(x, dens$x)
  iy <- findInterval(y, dens$y)
  ii <- cbind(ix, iy)
  return(dens$z[ii])
}

get_modobs <- function(df){
  tibble(mod = as.vector(df$pred), obs = df$obs)
}
list_modobs_listmodels <- purrr::map(rf_lgocv_flue$list_rf, ~get_modobs(.))
out_modobs <- list_modobs_listmodels %>%  bind_rows 

out_modobs$density <- get_density(out_modobs$obs, out_modobs$mod, n = 100)

library(Metrics)
bias_lab <- round(percent_bias(out_modobs$mod, out_modobs$obs),3) 
rsq_lab <- round(caret::postResample(out_modobs$mod, out_modobs$obs)['Rsquared'],2)
rmse_lab <- round(caret::postResample(out_modobs$mod, out_modobs$obs)['RMSE'],2)
n_lab <- length(out_modobs$mod)
lm <- lm(out_modobs$obs ~ out_modobs$mod)
slope_lab <- round(lm$coefficients[2],2)

# Significancia
summary(lm(out_modobs$obs ~ out_modobs$mod))

ggplot(out_modobs, aes(x=mod, y=obs)) +
  geom_point(aes(x=mod, y=obs, color = density)) +
  geom_smooth(method = "lm", se=FALSE, color="red", formula = y ~ x, cex=0.7) + 
  geom_abline(intercept=0, slope=1, linetype = "dashed", color="gray") +
  scale_color_viridis(option="magma") +
  theme_classic() +
  theme(axis.text=element_text(size=12, color="black"),
        axis.title=element_text(size=14),
        panel.border = element_rect(colour = "black", fill=NA)) +
  xlab("Predicted fLUE") + ylab("Observed fLUE") + 
  ylim(0,1.5) + xlim(0,1)  +
  annotate("text",x=0.15, y=1.50, label = paste("N ==", n_lab), parse=TRUE) +
  annotate("text",x=0.15, y=1.40, label = paste("R^2 ==" , rsq_lab), parse=TRUE) +
  annotate("text",x=0.15, y=1.30, label = paste("RMSE ==", rmse_lab), parse=TRUE) +
  annotate("text",x=0.15, y=1.20, label = paste("bias ==", bias_lab), parse=TRUE) + 
  annotate("text",x=0.15, y=1.10, label = paste("Slope ==", slope_lab), parse=TRUE) +
  annotate("text",x=0.27, y=1.10, label = paste("***"))

#### One Site time series: ###
sitename <- "AU-DaP"
one <- list_modobs_listmodels$`AU-DaP` 
ts_one <- ddf %>% filter(site == sitename ) %>% left_join(rename(one, flue=obs), by="flue") %>% 
  select(site, date, flue, is_flue_drought, mod)
plot(ts_one$flue~ts_one$date, type="l", ylab="Observed fLUE", xlab="Predicted fLUE", main=sitename)
lines(ts_one$mod~ts_one$date, col=2 )

library(reshape2)
ts <- melt(ts_one,id.vars = c("site","date","is_flue_drought"), measure.vars = c("flue", "mod") )
print(ggplot(ts, aes(x=date, y=value, group=variable)) +
        geom_line(aes(color=variable)) +
        scale_color_manual(values=c("black","red"),
                           name = NULL, labels = c("Observed fLUE","Predicted fLUE")) +
        theme_classic() + ggtitle(sitename)  +
        labs(x="Date", y="Unitless") + 
        theme(axis.text=element_text(size=12, color="black"),
              axis.title=element_text(size=14),
              panel.border = element_rect(colour = "black", fill=NA)) +
        scale_x_date(limits = as.Date(c('2000-01-01','2015-01-01'))) + labs(x="Date"))

```
## Vegetation class ##
```{r}

for(v in 3:length(cv)){
  ddf_veg <- ddf_sub %>% filter(classid == cv[v])
  
  # for(i in 1:length(predictores)){ # lenght(predictores)
  rf_lgocv <- wrap_ml( df = ddf_veg, 
                       nam_target = "flue", 
                       nam_group = "site",
                       method = "nnet",
                       train_method = "LGOCV",
                       predictors = c("ndvi", "evi","cci","pri","NIRv","APAR","temp"), # predictores[[1]], 
                       tune = TRUE,
                       inner = TRUE,
                       classification = FALSE
  )
  print(rf_lgocv$rf$results) # Promising: has accuracy of 0.81.
  save(rf_lgocv , file = paste("./data/NN_InsideVeg_Flue_mod",v,".Rdata",sep=""))
  
 list_modobs_listmodels <- purrr::map(rf_lgocv$list_rf, ~get_modobs(.))
out_modobs <- list_modobs_listmodels %>%
  bind_rows %>% 
  analyse_modobs2(mod = "mod", obs = "obs")
print(out_modobs$gg)

}

ddf_sub$biome[which(ddf_sub$classid %in% c("ENF","EBF","DBF"))] <- "forest"
ddf_sub$biome[which(ddf_sub$classid %in% c("SAV","GRA"))] <- "non-forest"
biome <- unique(ddf_sub$biome)

for(b in 2:2){
  ddf_veg <- ddf_sub %>% filter(biome == biome[b])
  
  # for(i in 1:length(predictores)){ # lenght(predictores)
  rf_lgocv <- wrap_ml( df = ddf_veg, 
                       nam_target = "flue", 
                       nam_group = "site",
                       method = "nnet",
                       train_method = "LGOCV",
                       predictors = c("ndvi", "evi","cci","pri","NIRv","APAR","temp"), # predictores[[1]], 
                       tune = TRUE,
                       inner = TRUE,
                       classification = FALSE
  )
  print(rf_lgocv$rf$results) # Promising: has accuracy of 0.81.
  # save(rf_lgocv , file = paste("./data/NN_InsideVeg_Flue_mod",b,".Rdata",sep=""))
  
 list_modobs_listmodels <- purrr::map(rf_lgocv$list_rf, ~get_modobs(.))
out_modobs <- list_modobs_listmodels %>%
  bind_rows %>% 
  analyse_modobs2(mod = "mod", obs = "obs")
print(out_modobs$gg)

}


```