---
title: "Site selection"
author: "Beni Stocker"
date: "4/15/2019"
output: html_document
---

## Site selection

Site selection was done based on:

1. Site where fLUE method worked and where clear soil moisture droughts were identified. I.e., site belongs to clusters cDD, cGR, or cLS as described in Stocker et al. (2018) *New Phytologist*.
2. Site was among the subset of homogenous sites, selected by Manuela Balzarolo. All sites with a homogenous surrounding are listed in file `data/FLUXNET-2015_Tier1/meta/fluxnet_quality_check_homogenous_OK_PRI_mbalzarolo.csv`. 

Reproduce it as follows:

Get sites where fLUE data is available
```{r}
library(readr)
library(dplyr)
df_flue <- read_csv("~/data/flue/flue_stocker18nphyt.csv")
df_flue_sites <- select(df_flue, site, cluster) %>% unique()
```

Add meta information for sites
```{r}
library(rsofun)
df_flue_sites <- df_flue_sites %>% rename(sitename=site) %>% left_join( rsofun::metainfo_Tier1_sites_kgclimate_fluxnet2015, by="sitename" )
```

Subset sites belonging to cluster cGR, cDD, or cLS
```{r}
df_sub <- df_flue_sites %>% filter(cluster %in% c("cGR", "cDD", "cLS"))
write_csv(df_sub, path = "~/data/flue/metainfo_sites_clusters_cGR_cDD_cLS_flue_fluxnet2015.csv")
```

Get list of sites with homogenous surrounding and subset fLUE sites based on that list
```{r}
df_homo <- read_csv("~/data/FLUXNET-2015_Tier1/meta/fluxnet_quality_check_homogenous_OK_PRI_mbalzarolo.csv")

df_flue_sites <- df_flue_sites %>% 
  mutate(homogenous_mbalzarolo = sitename %in% df_homo$sitename)

df_sub_homo <- df_flue_sites %>% 
  dplyr::filter( homogenous_mbalzarolo & cluster %in% c("cGR", "cDD", "cLS", "cNA") )
if (!dir.exists("./data")) system("mkdir data")
write_csv(df_sub_homo, path = "./data/sites2.csv")
```