---
title: "RSVI"
author: "Paula and Beni"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
# output:
#   pdf_document:
#     toc: true
#     toc_depth: 2
header-includes:
   - \usepackage{amsmath}
# bibliography: bibliography.bib
---

```{r}
source("MOD09_MODOC_filter.R")
source("remove_outliers.R")
source("gather_data.R")
source("align_events.R")
source("plot_rsvi.R")
source("plot_compare.R")
source("rsvi_sites.R")
source("add_scaled_rsvi.R")
source("add_normalised_rsvi.R")
source("get_consecutive.R")
# source("Index_vs_Index_isEvent.R")

library(dplyr)
library(lubridate)
library(readr)
library(ggplot2)
```

## Get data

Load all RSVI data from .Rdata file. Preprocessed by Paula. 

- Function "MOD09_MODOC_filter" combines MOD09GA and MODOCGA products for all sites (one CSV for each FLUXNET site) into one. The output is a csv file o it is in "MOD09GA_MODOCGA_filter_indices.Rdata" file (for more information see README - "MODIS Data information")

```{r}
## change path to file by hand here
path <-"C:/Users/Paula/Desktop/Pau/Ecologia terrestre/rsvi/data/"
## TODO: gather_data() should ideally take the paths to site-specific CSV files that were downloaded by Adria.
# ddf <- gather_data("/alphadata01/bstocker/data/modis_MOD09GA1km_fluxnet_cutouts/MOD09GA_MODOCGA_filter_indices.RData")
ddf <- gather_data("C:/Users/Paula/Desktop/Pau/Ecologia terrestre/rsvi/data/MOD09GA_MODOCGA_filter_indices.Rdata") %>% 
  ungroup()
```

## Site selection

Subset homogenous sites. Selection of sites is based on whether sites could be allocated to clusters in Stocker et al. (2018) and based on the selection by Manuela Balzarolo (see `site_selection_rsvi.Rmd`).
```{r}
df_homo <- read_csv("./data/sites.csv")
ddf <- ddf %>% filter( site %in% df_homo$sitename )
df_homo$sitename
```
## Scaling

Scaling is done with respect to the full time series of the RSVIs, not just the subset of data points just before and during drought events. Two methods are implemented:

- `"range"`: scales by range to within 0 and 1, where the range is from all values from all sites and dates.
- `"range_bysite"`: scales by range to within 0 and 1 by site, where the range is from values for each site separately.
```{r}
dovars <- colnames( dplyr::select( ddf, -date, -site ) )
ddf <- ddf %>% add_scaled_rsvi(dovars, method="range_bysite")
```


## Complement data

Add fLUE data.
```{r}
ddf <- read_csv("data/flue_stocker18nphyt.csv") %>% #/alphadata01/bstocker/data/flue/ (Benjamin)
  select(site, date, flue, is_flue_drought) %>% 
  right_join(ddf, by=c("site", "date"))
```

## Plot time series
Interesting: There is quite a trend in these indices, here for the site FR-Pue.
```{r}
# pdf(paste("Times_series.pdf",sep=""),width=10.84,height=5.30)
for(i in 1:length(unique(ddf$site))){
sitename <- unique(ddf$site)[i]
ddfsite <- ddf %>% filter(site == sitename)
flue_droughts <-  get_consecutive(ddfsite$is_flue_drought) 
if (nrow(flue_droughts)>0) {
flue_droughts$date_start <- ddfsite$date[flue_droughts$idx_start]
flue_droughts <- flue_droughts %>%  mutate(date_end = date_start + len) 

print(ddf %>% 
  tidyr::gather(rsvi, value, c(flue, ndvi, evi, cci, pri, NIRv)) %>% 
  filter(site==namesite) %>% 
  mutate(rsvi=factor(rsvi,levels=c("flue","ndvi", "evi", "cci", "pri", "NIRv"))) %>% 
  ggplot(aes(x=date, y=value)) +
    facet_grid(rows=vars(rsvi), scales = "free_y") +
    geom_rect(
    data = flue_droughts, 
    aes(x = NULL,y = NULL, xmin=date_start, xmax=date_end, ymin=-Inf, ymax=Inf),
    fill=("#e8c745"), alpha=0.7, #rgb(0,0,0,0.3) 
    color=NA) +
  geom_line() + theme_bw() + ggtitle(sitename) +
  scale_x_date(limits = as.Date(c('2000-01-01','2015-01-01'))))
}else{
 print(ddf %>% 
  tidyr::gather(rsvi, value, c(flue, ndvi, evi, cci, pri, NIRv)) %>% 
  filter(site==namesite) %>% 
  mutate(rsvi=factor(rsvi,levels=c("flue","ndvi", "evi", "cci", "pri", "NIRv"))) %>% 
  ggplot(aes(x=date, y=value)) +
    facet_grid(rows=vars(rsvi), scales = "free_y")  +
  geom_line() + theme_bw() + ggtitle(namesite) +
  scale_x_date(limits = as.Date(c('2000-01-01','2015-01-01'))))
}

}
# dev.off()
```
```{r}
sitename <- "FR-Pue"
ddfsite <- ddf %>% filter(site == sitename)
flue_droughts <-  get_consecutive(ddfsite$is_flue_drought) 
flue_droughts$date_start <- ddfsite$date[flue_droughts$idx_start]
flue_droughts <- flue_droughts %>%  mutate(date_end = date_start + len) 

ddf %>% 
  tidyr::gather(rsvi, value, c(flue, pri)) %>% 
  filter(site==sitename) %>% 
  ggplot(aes(x=date, y=value)) +
  geom_line(aes(group=rsvi)) +
  theme_bw() +
  facet_grid(rows=vars(rsvi), scales = "free_y") +
    geom_rect(
    data = flue_droughts, 
    aes(x = NULL,y = NULL, xmin=date_start, xmax=date_end, ymin=-Inf, ymax=Inf),
    fill=rgb(0,0,0,0.3), 
    color=NA) 

```

## Align by drought event
```{r}
## Get fLUE Stocker et al., 2018 publicly available data here: https://zenodo.org/record/1158524#.W_bNMZNKjOQ

df_flue <- readr::read_csv("data/flue_stocker18nphyt.csv") %>% #/alphadata01/bstocker/data/flue/ Beni
  dplyr::select(-year, -doy, -cluster) %>% 
  dplyr::rename( isevent = is_flue_drought )

## Rearrange data
out_align <- align_events( 
  ddf, 
  select(df_flue, site, date, isevent), 
  dovars, 
  leng_threshold=10, 
  before=10, after=80, nbins=9
  )

## Raw data time series
out_align$df_dday_agg_inst %>% filter(site == sitename) %>%
  ggplot(aes(x=dday, y=pri_median)) +
  geom_line() 

##  Raw data, aligned by drought events
out_align$df_dday %>% #filter(site == sitename) %>%
  ggplot(aes(x=dday, y=pri)) +
  geom_line(aes(group=inst)) +
  facet_wrap(~site, scales = "free_y") + ggtitle("RSVI")

##  dsRSVI data, aligned by drought events
out_align$df_dday %>% #filter(site == sitename) %>%
  ggplot(aes(x=dday, y=dspri)) +
  geom_line(aes(group=inst)) +
  theme_bw() +
  facet_wrap(~site, scales = "free_y") + ggtitle("sdRSVI")

```
Not clear to me why the curve is not centered around 1 for dday between -10 and 0 (zero-bin). Division by median of value in zero-bin is done in `align_events()`.

## Normalisation

df_flue <-  readr::read_csv("data/flue_stocker18nphyt.csv") %>%
  dplyr::select(-year, -doy, -cluster) %>%
  dplyr::rename( isevent = is_flue_drought )

## Get homogeneous sites:
homo_sites <- read.csv("data/sites.csv") %>%
  rename(site = sitename)
homo_sites <- as.character(unique(homo_sites$site))

ddf <- ddf[which(ddf$site %in% homo_sites),] %>% ungroup()

## Rearrange data. Function returns list( df_dday, df_dday_aggbydday )
dovars <- colnames( dplyr::select( ddf, -date, -site ) ) # this does not necessarily work with the data's column names you have in 'ddf'

# dovars <- colnames(ddf)[3:14]
out_align <- align_events(ddf, df_flue, dovars, leng_threshold = 10, before=20, after=60, nbins=8, do_norm=FALSE )


Add normalised RSVIs to the full time series, using the median in the zero-bin per site and RSVI. This information is returned by function `align_events()`.
```{r}
sdovars <- paste0("s", dovars)
ddf <- ddf %>% add_normalised_rsvi(sdovars, out_align$norm) 
```


## Plots aligned by site

Data is aggregated across multiple drought events (column `inst`).
```{r}
median <- out_align$df_dday_agg_inst %>%
  select(site, dday, ends_with("median")) %>% 
  tidyr::gather(rsvi, median, ends_with("median")) %>% 
  mutate(rsvi=stringr::str_replace(rsvi, "_median", "") )
q33 <- out_align$df_dday_agg_inst %>%
  select(site, dday, ends_with("q33")) %>% 
  tidyr::gather(rsvi, q33, ends_with("q33")) %>% 
  mutate(rsvi=stringr::str_replace(rsvi, "_q33", "") )
q66 <- out_align$df_dday_agg_inst %>%
  select(site, dday, ends_with("q66")) %>% 
  tidyr::gather(rsvi, q66, ends_with("q66")) %>% 
  mutate(rsvi=stringr::str_replace(rsvi, "_q66", "") )
df_dday_agg_inst <- median %>%
  left_join(q33, by=c("site","dday", "rsvi")) %>% 
  left_join(q66, by=c("site","dday", "rsvi"))

## Example for one site
df_dday_agg_inst %>% 
  filter(site=="US-SRM") %>% 
  filter(rsvi %in% c("flue","dsndvi", "dsevi", "dscci", "dspri", "dsNIRv")) %>% 
  ggplot(aes(x=dday, y=median)) +
  geom_line() +
  labs(x="Day after drought onset", y="Unitless") +
  geom_ribbon(aes(ymin=q33, ymax=q66), alpha=0.3) +
  facet_wrap( ~ rsvi)
```


## Plot aligned and aggregated sites


Absolute values, aggregated across sites and events
```{r}
median <- out_align$df_dday_agg_inst_site %>%
  select(dday, ends_with("median")) %>% 
  tidyr::gather(rsvi, median, ends_with("median")) %>% 
  mutate(rsvi=stringr::str_replace(rsvi, "_median", "") )
q33 <- out_align$df_dday_agg_inst_site %>%
  select(dday, ends_with("q33")) %>% 
  tidyr::gather(rsvi, q33, ends_with("q33")) %>% 
  mutate(rsvi=stringr::str_replace(rsvi, "_q33", "") )
q66 <- out_align$df_dday_agg_inst_site %>%
  select(dday, ends_with("q66")) %>% 
  tidyr::gather(rsvi, q66, ends_with("q66")) %>% 
  mutate(rsvi=stringr::str_replace(rsvi, "_q66", "") )
df_dday_agg_inst_site <- median %>%
  left_join(q33, by=c("dday", "rsvi")) %>% 
  left_join(q66, by=c("dday", "rsvi"))

df_dday_agg_inst_site %>% 
  filter(rsvi %in% c("flue","ndvi", "evi", "cci", "pri", "NIRv")) %>% 
      mutate(rsvi=factor(rsvi,levels=c("flue","ndvi", "evi", "cci", "pri", "NIRv")))  %>% 
  ggplot(aes(x=dday, y=median)) +
  geom_line() +
  labs(x="Day after drought onset", y="Unitless") +
  geom_ribbon(aes(ymin=q33, ymax=q66), alpha=0.3) +
  facet_wrap(~rsvi, scales = "free_y")

df_dday_agg_inst_site %>% 
  filter(rsvi %in% c("flue","sndvi", "sevi", "scci", "spri", "sNIRv")) %>% 
    mutate(rsvi=factor(rsvi,levels=c("flue","sndvi", "sevi", "scci", "spri", "sNIRv"))) %>% 
  ggplot(aes(x=dday, y=median)) +
  geom_line() +
  theme_bw() +
  labs(x="Day after drought onset", y="Unitless") +
  geom_ribbon(aes(ymin=q33, ymax=q66), alpha=0.3) +
  facet_wrap(~rsvi, scales = "free_y")

df_dday_agg_inst_site %>% 
  filter(rsvi %in% c("flue","dsndvi", "dsevi", "dscci", "dspri", "dsNIRv")) %>% 
      mutate(rsvi=factor(rsvi,levels=c("flue","dsndvi", "dsevi", "dscci", "dspri", "dsNIRv"))) %>% 
  ggplot(aes(x=dday, y=median)) +
  geom_hline(yintercept=1,col="gray") +
  theme_classic() +
  geom_line() +
  labs(x="Day after drought onset", y="Unitless") +
  geom_ribbon(aes(ymin=q33, ymax=q66), alpha=0.3) +
  facet_wrap(~rsvi) 
```

## Plot by vegetation type
- Add vegetation type to data and do evaluations with data aggregated by vegetation type - the way you've done it before.
```{r}
## Vegetation type - add info
load(paste(path,"metainfo_sites_fluxnet2015.Rdata",sep=""))
metainfo_sites_fluxnet2015 <- as_tibble(metainfo_sites_fluxnet2015)

# set of RSVI:
vars <- c("flue","dsndvi", "dsevi", "dscci", "dspri", "dsNIRv")

df_dday_agg_inst_veg <- merge(df_dday_agg_inst, metainfo_sites_fluxnet2015[,c(1,5)], by.x="site", by.y="mysitename") 
nclass <- unique(df_dday_agg_inst_veg$classid)

# Median by classid (nomalized on 1)
df_dday_agg_inst_veg %>%  group_by( dday, classid, rsvi ) %>% 
  summarise_at( vars(one_of("median","q33","q66")), funs(median( ., na.rm=TRUE))) %>%
  filter( !is.na( dday ) ) %>%
  filter(rsvi %in% vars) %>% 
      mutate(rsvi=factor(rsvi,levels=vars)) %>% 
  ggplot(aes(x=dday, y=median, group=classid)) + # If we want the different sites: ,group=site
  geom_vline(xintercept=0,col="gray") + geom_hline(yintercept=1,col="gray") +
  geom_line() + geom_ribbon(aes(ymin=q33, ymax=q66), alpha=0.3) +
  # xlim(-10, 40) + 
  theme_bw() +
  facet_grid(rsvi~classid,  scales = "free_y") +
  labs(x="Day after drought onset", y="Unitless")

# All sites
df_dday_agg_inst_veg %>% 
  filter(rsvi %in% vars) %>% 
      mutate(rsvi=factor(rsvi,levels=vars)) %>% 
  ggplot(aes(x=dday, y=median, group=site)) + # If we want the different sites: ,group=site
  geom_hline(yintercept=1,col="gray") + geom_vline(xintercept=0,col="gray") +
  labs(x="Day after drought onset", y="Unitless") +
  geom_line(aes(col=site)) +
  geom_ribbon(aes(ymin=q33, ymax=q66), alpha=0.3) +
  # xlim(-10, 40) +
  theme_bw() +
  facet_grid(rsvi~classid,  scales = "free_y")
```
```{r}
# Median by classid (nomalized on 1) and by site
df_dday_agg_inst_veg %>%  group_by( dday, classid, rsvi ) %>% 
  summarise_at( vars(one_of("median","q33","q66")), funs(median( ., na.rm=TRUE))) %>%
  filter( !is.na( dday ) ) %>%
  filter(rsvi %in% vars) %>% 
      mutate(rsvi=factor(rsvi,levels=vars)) %>% 
  ggplot(aes(x=dday, y=median, group=rsvi, color=rsvi)) + # If we want the different sites: ,group=site
  geom_vline(xintercept=0,col="gray") + geom_hline(yintercept=1,col="gray") +
  geom_line() + # geom_ribbon(aes(ymin=q33, ymax=q66), alpha=0.3) +
  # xlim(-10, 40) + 
  theme_bw() +
  facet_wrap(~classid,  scales = "free_y") +
  labs(x="Day after drought onset", y="Unitless")

```

## Next steps
- According to this evaluation, CCI and PRI vary very little during drought conditions but are clearly correlated with other RSVIs. Is this correlation affected whether data is in a drought or not? Below a quick look at how EVI and PRI are correlated and how this relationship is affected by the factor `is_flue_drought`. There might be some information here...
```{r}
ddf %>% 
  filter(!is.na(is_flue_drought)) %>% 
  ggplot(aes(x=evi, y=cci, color=is_flue_drought)) +
  scale_colour_discrete(name  ="Is fLUE Drought?",
                            labels=c("No Drought","Drought")) +
  theme_bw() +
  labs(x="EVI", y="CCI") +
  geom_point(alpha=0.2)
```

- Complement the data with meteorological variables, measured at the FLUXNET sites. 
```{r}
load("data/obs_eval_NT.Rdata") # adjust path /Users/benjaminstocker/eval_pmodel/
ddf <- ddf %>% left_join(rename(obs_eval_NT$ddf, site=sitename), by=c("site", "date"))

ddf %>% 
  filter(!is.na(is_flue_drought)) %>% 
  ggplot(aes(x=evi, y=pri, color=is_flue_drought)) +
    scale_colour_discrete(name  ="Is fLUE Drought?",
                            labels=c("No Drought","Drought")) +
  geom_point(alpha=0.2)


```
```{r}
ddf %>% 
  filter(!is.na(is_flue_drought)) %>% 
  ggplot(aes(x=ndvi, y=cci, color=is_flue_drought)) +
  geom_point(alpha=0.2)

```
## Index vs Index: pdf attached, it has problems here
```{r}
# Temperature filter (<5ºC) and aggregated by vegetation type
ddf_veg <- ddf %>% 
  left_join(rename(metainfo_sites_fluxnet2015[,c(1,5)], site=mysitename), by="site")

nclass <- unique(ddf_veg$classid)
# Index_vs_Index_isEvent() 
```
- Based on the effect of the factor `is_flue_drought` on the relationship between RSVIs, we may try to predict this factor using the information in RSVIs. Two methods could be tried out:
  
    - K-means clustering with `k=2`, then check whether clusters are congruent with `is_flue_drought`. It looks like indeed, most of the drought-days can correctly be identified as such based on the RSVIs:
```{r}
ddf_cluster <- ddf %>%
  # filter(temp>5) %>%
  select(is_flue_drought, one_of(dovars)) %>% # Add temperature and PPFD here if you like. 
  drop_na()
outkmeans <- kmeans( ddf_cluster, 2 )
ddf_cluster %>% 
  mutate(cluster=as.factor(outkmeans$cluster-1)) %>%
  group_by(cluster, is_flue_drought) %>% 
  summarise(count=n()) %>% 
  ggplot(aes(x=cluster, y=count, fill=is_flue_drought)) +
  geom_bar(stat="identity", position=position_dodge())

outkmeans

```  
Adding temperature and PPFD (PPFDxfAPAR to get the "absorbed" light, not incident light)) in the mix of variables used for K-means but the proportions didn't in each cluster change
```{r}
ddf_cluster <- ddf %>%
  # filter(temp>5) %>%
  mutate (PPFD = ppfd_fluxnet2015 * fapar) %>%
  select(is_flue_drought, dovars, PPFD, temp, prec_fluxnet2015) %>% 
  drop_na()
outkmeans <- kmeans( ddf_cluster, 2 )
ddf_cluster %>% 
  mutate(cluster=as.factor(outkmeans$cluster-1)) %>%
  group_by(cluster, is_flue_drought) %>% 
  summarise(count=n()) %>% 
  ggplot(aes(x=cluster, y=count, fill=is_flue_drought)) +
  geom_bar(stat="identity", position=position_dodge()) 
outkmeans
```  

  - Random-forest, supervised machine-learning with `is_flue_drought` as target and RSVIs (plus possibly other meteorological variables) as predictors. The `caret` R package offers a nice framework to use machine-learning models. Let's speak before diving into this.
  
## Random-forest
```{r}

```
- Look at the mean seasonality. A hypothesis to look at is whether RSVIs co-vary and whether this covariation is affected by the factor `is_flue_drought`. A quick look at that:
```{r}

dsdovars <- paste0("d", sdovars)

for (i in 1:length(unique(ddf$site))){
sitename <- unique(ddf$site)[i]
tmp <- ddf %>% 
  filter(site==sitename) %>% 
  mutate(doy=lubridate::yday(date)) %>% 
  group_by(site, doy) %>% 
  summarise_at(
    vars("is_flue_drought", one_of(dsdovars)),
    funs(mean(., na.rm=TRUE)) ) %>% 
  tidyr::gather("rsvi", "value", c("is_flue_drought", dsdovars))

print(ggplot() +
  geom_vline(data=filter(tmp, rsvi == "is_flue_drought"), aes(xintercept=doy, alpha=0.5*value), size=0.2) +
  geom_line(data=filter(tmp, !(rsvi == "is_flue_drought")), aes(x=doy, y=value, color=rsvi), size=1) +
    ggtitle(sitename) + 
  theme_bw())
}
# plot_compare(out_align$df_dday_aggbydday, scale = FALSE, method = "zscore")
# # One site
# out <- plot_rsvi_bysite( "FR-Pue", ddf )
# rsvi_sites(out_align$df_dday, name_site="FR-Pue")

```

